Parsing Postfix Log Files

### 2009-08-27 doc/logparser-results.tex
Explain where the 93 log files come from; required by Howard Hamilton.

The \numberOFlogFILES{} log files used when generating statistics have
fairly consistent sizes and contents, except for two groups of log files:
22 \& 62--68.  Median log file size is
\input{build/include-median-file-size}, containing
\input{build/include-median-number-of-log-lines} log lines, with a median
of \input{build/include-median-mails-accepted-over-smtp} mails accepted
each weekday; large scale mail servers would accept many more mails and
consequently generate much larger log files.  \Graphref{parsing time vs log
file size vs number of log lines graph} shows the parsing time in seconds,
log file size in MB, and number of log lines in tens of thousands, for each
of the \numberOFlogFILES{} log files.  Parsing time is plotted against
number of log lines in \graphref{Parsing time plotted against number of log
lines}, and against log file size in \graphref{Parsing time plotted against
log file size}; the points on both graphs appear to form straight lines,
but they actually curve downwards slightly as they move to the right.

>>>>

The \numberOFlogFILES{} log files used in this chapter were generated on
the School of Computer Science and Statistics' mail server from 2007/01/26
to 2007/04/28.  The \numberOFlogFILES{} log files have fairly consistent
sizes and contents, except for two groups of log files: 22 \& 62--68.
Median log file size is \input{build/include-median-file-size}, containing
\input{build/include-median-number-of-log-lines} log lines, with a median
of \input{build/include-median-mails-accepted-over-smtp} mails accepted
each weekday; large scale mail servers would accept many more mails and
consequently generate much larger log files.  \Graphref{parsing time vs log
file size vs number of log lines graph} shows the parsing time in seconds,
log file size in MB, and number of log lines in tens of thousands, for each
of the \numberOFlogFILES{} log files.  Parsing time is plotted against
number of log lines in \graphref{Parsing time plotted against number of log
lines}, and against log file size in \graphref{Parsing time plotted against
log file size}; the points on both graphs appear to form straight lines,
but they actually curve downwards slightly as they move to the right.
